Comprehensive optical and data management infrastructure for high-throughput light-sheet microscopy of whole mouse brains

### 2015-03-25 latex-style-files-spie-manuscript/manuscript_submission.tex
bob

\affiliation{\supscrsm{a}European Laboratory for Non-linear Spectroscopy (LENS), University of Florence, Italy\\
\supscrsm{b}Department of Physics and Astronomy, University of Florence, Italy\\
\supscrsm{c}National Institute of Optics, National Research Council, Italy\\
\supscrsm{d}International Center for Computational Neurophotonics (ICON Foundation), Italy\\
\supscrsm{e}Integrated Research Centre, University Campus Bio-Medico of Rome, Italy\\
%\supscrsm{f}Distrio, Amsterdam, The Netherlands
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{abstract}
The comprehensive mapping and quantification of neuronal projections in the central nervous system requires high-throughput imaging of large volumes with microscopic resolution. We have developed a confocal light-sheet microscope that has been optimised for the 3D imaging of structurally intact clarified whole-mount mouse brains. Here we describe the optical and electro-mechanical arrangement of the microscope and give details on the organisation of the microscope management software. The software orchestrates all components of the microscope, coordinates critical timing and synchronisation and has been written in a versatile and modular structure using the LabVIEW language.  It can easily be adapted and integrated to other microscope systems and has been made freely available to the light-sheet community. The tremendous amount of data routinely generated by light-sheet microscopy further requires novel strategies for data handling and storage. To complete the full imaging pipeline of our high- throughput microscope we further elaborate on big data management from the data streaming of raw images up to stitching and visualisation of 3D data sets. The meso-scale neuroanatomy imaged at micron-scale resolution in those datasets allows characterization and quantification of neuronal projections in unsectioned mouse brains. 
\end{abstract}

%>>>> Include a list of up to six keywords after the abstract
\keywords{Light-sheet microscopy, whole brain, data management, software management, imaging pipeline, high-throughput imaging}

%>>>> Include contact information for corresponding author
{\noindent \footnotesize{\bf Address all correspondence to}: First author, University Name, Faculty Group, Department, Street Address, City, Country, Postal Code; Tel: +1 555-555-5555; Fax: +1 555-555-5556; E-mail:  \linkable{myemail@university.edu} }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{spacing}{2}   % use double spacing for rest of manuscript

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}%funnel shape
\label{sect:intro}

The highly ambitious project of mapping and understanding each and every neuronal projection in the whole brain has been moved to feasible reality by the recent advent of light-sheet fluorescent microscopy (LSFM)\cite{Huisken2004,Dodt2007,Keller2012}. With this technique 3D data sets can be acquired with a resolution that is high enough to identify neurons and their dendritic, axonal features in time scales which are no longer the bottle neck of high-throughput acquisition. In LSFM, the sample is illuminated with a thin sheet of light confined into the focal plane of the detection objective, which collects the fluorescence emission along an axis perpendicular to the illumination plane\cite{Huisken2009}. This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel due to its wide-field detection and affords intrinsic optical sectioning due to the light-sheet illumination. Consequently fluorophores outside the light-sheet are neither bleached nor contribute blurring out-of-focus noise. Together these attributes cause a high spatio-temporal resolution and an excellent signal to noise ratio in LSFM.

Several challenges remain to be overcome, however, to allow fast and, most of all, systematic production of reliable datasets and their meaningful interpretation to further our understanding of neuronal networks. Those challenges include fast, cheap and reproducible sample preparation and mounting, automated image acquisition and, most crucially, storage, interpretation and analysis of the vast data sets light-sheet microscopy routinely produces. The mapping and understanding of this ``big data" is an immense task that requires the expertise of computer scientists to employ fully automated post-processing, for example, to do cell counting or blood vessel segmentation. On the other hand, the imaging of large, intrinsically opaque samples in LSFM necessitates clearing protocols based on refractive index matching which render the tissue transparent. Therefore technological advances in LSFM need to be matched by novel development in the area of information- and biotechnology.

Here we will present a state-of-the-art light-sheet microscope, as it is implemented in our lab, that is especially well suited to acquire 3D data sets of large clarified and structurally intact mouse brains. The LSFM features double-sided illumination with a digitally scanned light-sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$) immersed and freely movable samples. After briefly introducing the optical setup we explain how to prepare and mount the samples for stable, 3D imaging for several days. In addition, a full description of the control hardware and software is presented. The microscope software coordinates every microscope component and ensures critical timing and synchronisation between those components. %The software code has been implemented using a versatile and modular scheme in the LabVIEW language and has been made freely available to the light-sheet community. 
We further give a systematic and robust approach to handle, store and analyse light-sheet microscopy data of several terabytes. To conclude the comprehensive and high-throughput imaging pipeline we furthermore elaborate on stitching and visualisation of large 3D data sets. The imaging capabilities of our light-sheet microscope are exemplified with tomographies of whole transgenic mouse brains.

%\begin{figure}
   %\begin{center}
   %\begin{tabular}{c}
   %\includegraphics[width=\textwidth]{PanelSampel.eps}
   %\end{tabular}
   %\end{center}
   %\caption{\label{fig:Panel0} (A) Schematic of light-sheet microscopy. The sample is illuminated with a planar light-sheet (blue) perpendicular to fluorescence detection (green). (B) Mounting of a clarified, fluorescently labelled brain. The brain is glued onto a coverslip and inserted into an adapter that slides into a Teflon cylinder.} 
   %\end{figure}

@@

		\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{frame1.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:excitation} (A) Topview of the excitation path. The galvo scanners are mounted above periscopes. LP: long-pass filter, I: iris, AOTF: acousto-optical tunable filter, LM: laser modulator, PBS: polarisation beam splitter. Green dotted: detection path. (B) Oblique view of the microscope. A custom-made breadboard serves to mount the sample chamber and objectives at an elevated height and features two circular holes at the edges for the periscopes and a large central cut-out for the translation stages. A second breadboard is used for the camera.} 
   \end{figure}

\subsection{Laser unit}		
The custom-made confocal light-sheet microscope is equipped with 5 linearly polarised, continuous-wave lasers for fluorescence excitation (Fig. \ref{fig:excitation},A). The wavelengths were chosen to excite the most common fluorophores (see Table \ref{tab:optomechanics} for the manufacturer and specifications of opto-mechanical components). The laser light from each laser is first collimated and expanded with a telescope (f140, f200) and then combined into a common path with a beam steering mirror and a long-pass filter (Semrock, LaserMUX\texttrademark\ series). An acousto-optical tunable filter (AOTF) acts as fast ($\mu s$) electronically tunable filter and intensity modulator. %which uses the acousto-optical interaction inside an anisotropic medium to select and transmit any combination of up to four of the laser lines. The radio-frequency applied on the AOTF transducer controls the wavelength being transmitted into the first order and the radio-frequency amplitude allows to adjust the transmitted light intensity. 
Due its nonlinear response we measured the AOTF light transmittance for each wavelength as a function of radio frequency amplitude and determined a look-up table to linearise the output. The zero order light is blocked by an iris. An electro-optical laser modulator (EOM) acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$. %The wavelength-dependent high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step amplification system. First, a low voltage analog signal from the data acquisition and generation (DAQ) board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier. 
A digital line is used to switch between the voltage levels, allowing control of the frequency with which the polarisation is changed (see also section \ref{sec:timing} on timing).

\subsection{Illumination unit}		
The light impinges onto a polarising beam splitter cube which splits the excitation light depending on its polarisation into one of the two identical excitation arms. The beam diameter is reduced with a telescope (f350, f200) whose telecentric plane coincides with the mirrored surface of a galvanometric scanner (galvo). Both galvos are mounted on a custom made optical breadboard which features two circular holes to pass the periscopic beams and a large central cut-out for the sample chamber and motor stages.

Each scan mirror surface is re-imaged with a telescope (f50, f100) onto the back aperture of a long working distance low magnification objective (Nikon, 10x 0.3NA WD 17.5mm).  The galvos are in planes conjugate with the back focal plane of their respective excitation objective to ensure that a tilt angle of the galvo converts into a lateral translation of the Gaussian beam across the specimen. The two excitation objectives are designed for air immersion but are immersed into the clearing solution (n=1.45) within the sample chamber. A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the front lens elements from the clearing agent. A guide to align objectives to a common focus can be found in the supplementary information. The light-sheet is generated digitally\cite{Keller2008a,Keller2008b} by scanning the excitation beam across the focal plane of the detection objective. This generates incoherent illumination resulting in fewer artefacts. %cite{StelzerNatMeth2014}.
Additionally each line in specimen is illuminated with the same intensity creating a homogeneous light-sheet which is particularly advantageous for the quantitative and qualitative investigation of large samples in their entirety.

@@

%In its simplest form, the fluorescence detection unit of a light-sheet microscope is a conventional wide-field microscope: an objective lens, a fluorescent filter and a tube lens form an image on a wide-field detector. 
Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions. The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP, 25x, 1.0NA, effective focal length 7.2 mm, working distance 8mm). %To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging. 
A tube lens of 200mm creates an image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a chip of over 4 megapixels. %In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other. 
The cell size of the OrcaFlash is $p^2= (6.5\micro m)^2$ over an active area of $r^2= (13.3mm)^2$. With a 200mm tube lens the field of view (FOV) in the sample is $(480\micro m)^2$ (see also Table \ref{tab:resolution} for relevant formulas).

In the camera's rolling shutter data acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor\cite{Baumgart2012}. With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($t_{\text{shutter}}=9.7\micro s$) the entire frame of 2048 horizontal lines is activated within 19.86ms. For instance, setting the line exposure time to $t_{\text{exp}}=0.3ms$ results in $l=\nicefrac{t_{\text{exp}}}{t_{\text{shutter}}}\approx31$  lines being simultaneously exposed at any time. This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of $s_{\text{object}}=\nicefrac{l p}{M_{\text{eff}}}= 7.2 \micro m $ in the sample space, where $M_{\text{eff}}$ is the effective magnification of the detection objective. With the given values of line exposure and line read out time, the camera acquires images at a frame rate of  $R_{\text{frame}} = \nicefrac{1}{(\#_{\text{horiz. lines}}*t_{\text{shutter}}+t_{\text{exp}})} \approx 50Hz$.

The camera was run as master in the internal trigger mode and a synchronisation pulse generated with the exposure of each new line was used as an output trigger for the DAQ board which was operated as slave. The saw-tooth driving signal for the galvo mirrors was generated by the DAQ and synchronised with the pixel line reset pulses from the camera to achieve confocal line detection\cite{Baumgart2012} (see also section \ref{sec:timing} on synchronisation). %Any deviation from precise synchronisation results in image artefacts and severely degraded image contrast. The confocal resolution can be changed at run-time by changing the user-defined line exposure time and with it the rolling shutter width, that is the number of horizontal pixel lines simultaneously exposed.

\subsection{Sample mounting and motion}
\label{sec:mounting}
%Biological tissue is, bar of very few exemptions like the cornea or zebrafish larvae, highly scattering. Scattering is the deflection of light rays due to the heterogeneous mixture of cells and sub-cellular structures with varying refractive indices. Rayleigh scattering, the nearly isotropic and strongly wavelength dependent scattering of light by particles much smaller than the wavelength of light, and Mie scattering, which occurs on cellular structures such as organelles and other refractive structures which are larger than the wavelength of light, far outweigh absorption and cause most biological tissues to be opaque. In the visible spectrum, the scattering of fluorescence photons is dominant over ballistic fluorescence such that for the imaging of large samples optical clearing methods based on refractive index matching have been employed. These methods involve several chemical sample preparation steps to generate transparent yet structurally and anatomically intact tissue.
%
%A successful optical clearing method not only renders the tissue transparent but also causes neither quenching of protein fluorescence nor tissue distortion and is compatible with repetitive immunostaining. A very promising method called CLARITY\cite{Chung2013,Tomer2014} transforms tissue into a nanoporous, hydrogel-hybridized, lipid-free form. Crucially for high through-put clearing and imaging of large samples, the protocol, however, is ideally also fast, easy and cheap. Our lab therefore development a versatile, simple, rapid and inexpensive clearing method based on a water-soluble agent, 2,2'-thiodiethanol (TDE) which in combination with CLARITY allows for the optical clearing of entire mouse brains or human biopsies. With this protocol (see [cite Irene] for a detailed description) a mouse brain (Figure\ref{fig:Panel1},B) takes 1 month to clear at a costs of \$XY.

@@

We designed a cubic water-tight sample chamber (Fig. \ref{fig:frame2},A) that allows access from all six sides while maintaining the 3D integrity of large clarified and fluorescently-labelled mouse brains. The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Fig. \ref{fig:frame2},B). Connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders. In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Fig. \ref{fig:frame2},C). The clarified brains are imaged immersed in clearing solution composed of 63\% 2,2'-thiodiethanol (TDE) in Phosphate buffered saline (PBS) and a refractive index of $\approx 1.45$\cite{Costantini}. To fill the entire volume of the sample chamber approximately 150ml clearing solution are needed. A motorized x-, y-, z-, $\theta$-stage (see Table \ref{tab:optomechanics}) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Fig. \ref{fig:frame2},D). Illumination and detection axes are horizontal while sample rotation occurs around the vertical axis.

To elucidate neuronal projections in structurally intact tissue it is paramount to be able to image centimeter-sized clarified samples, such as mouse brains, with high resolution in whole mount preparation. %While promising clearing protocols are well documented in literature\cite{Chung2013,Tomer2014}, the question of sample preparation and mounting in light-sheet microscopy is not trivial but requires novel approaches to such extent that it is becoming a separate field of research and very diverse strategies such as FEP tubes, 3D printed chambers and Quartz cuvettes have been reported\cite{Kaufmann2012,Pitrone2013,Olarte2012,Tomer2014}, however, these approaches are limited to much smaller sample volumes. 
The problem of sample mounting in a light-sheet microscope arises from the fact that optical access to the sample is required from 3-4 planar sides leaving only two opposing sides to insert, fix and move the sample. %Most commonly the vertical direction is chosen. 
Stable mounting is hereby a key concern as a whole brain tomography can require image acquisition in excess of 24 hours and the effects of gravity, tissue shrinking/expansion and evaporation of the clearing solution over such time spans might have to be considered.

For the acquisition of whole brain data sets, we fix a clarified and fluorescently-labelled mouse brain with super glue to a coverslip (Fig. \ref{fig:frame2},E). The brain is oriented along its axial orientation with the olfactory bulbs at the top and the cerebellum at the bottom of the coverslip. The coverslip is slid into a bottom adaptor and tightened with a plastic-capped grub screw. The bottom adaptor is inserted into a Teflon cylinder with the coverslip being positioned on the far side of the detection objective. Three different slits in the adapter correspond to varying distances to the detection objective and give variability in sample thickness for example to allow also for the mounting of rat brain hemispheres.

\subsection{Optical characterisation}

\subsubsection{Theoretical considerations}

The optical properties of a microscope can be summarised by the point-spread function (PSF), which is the image of a point source in object space. In particular, the radial (i.e. perpendicular to the detection axis) and axial (i.e. parallel to the detection axis) resolution of the microscope can be quantified with the full width at half-maximum (FWHM) of the PSF itself along the chosen direction (see Fig. \ref{fig:origin},A). In a light-sheet microscope axial and radial resolution are determined by the numerical aperture (NA) of the illumination and detection optics respectively. The radial PSF is a standard Airy function whose FWHM is given by:

\begin{equation}
\text{FWHM}_{\text{radial}} \simeq \frac{0.51 \lambda_0}{\text{NA}_{\text{d}}},
\end{equation}
$\lambda_0$ being the wavelength in vacuum and $\text{NA}_{\text{d}}$ the NA of the detection objective. The axial resolution is dominated by the thickness of the light-sheet which for high NA detection objectives is usually larger than the depth of field of the detection objective. If Gaussian beams are used for illumination, the thickness of the light-sheet can be calculated by the well-known formulas of Gaussian optics\cite{Teich}. The radius of the beam waist is given by:

@@

\begin{equation}
\text{FWHM}_{\text{axial}} \simeq 1.177 w_0.
\end{equation}
The thickness of the light-sheet is not constant throughout the FOV due to the limited depth of focus of the Gaussian beam. The latter can be quantified by the confocal parameter $b$, which is the distance along which the beam $1/e^2$ radius remains relatively constant and smaller than $\sqrt{2} w_0$:

@@

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{origin.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:origin} Optical characterisation. (A) Exemplary lateral and axial intensity profiles of sub-resolution beads and fits to Gaussian. (B) For each unit 10 bead profiles were fitted in all three dimensions and their FWHM was averaged. (C) The signal to noise ratio.} 
\end{figure}

@@

For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) we acquired image stacks of nanometric fluorescent beads ($0.51 \micro m$ diameter, Bangs Laboratories). The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, was not affected by the confocal slit width on the camera (Fig. \ref{fig:origin},B). The lateral and axial FWHMs were $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14) \micro m$ respectively, averaged through stack depths and confocal slit widths. The experimentally determined lateral FWHM was larger than the theoretically calculated value of $0.26 \micro m$ by a factor of four. The discrepancy is likely caused by higher order aberrations introduced by the gel embedding the fluorescent beads exacerbated by the high NA of our detection objective\cite{Schwertner2004,Schwertner2007}.

@@

\section{Data Management}

>>>>

\affiliation{\supscrsm{a}European Laboratory for Non-Linear Spectroscopy (LENS), University of Florence, Italy\\
\supscrsm{b}Department of Physics and Astronomy, University of Florence, Italy\\
\supscrsm{c}National Institute of Optics, National Research Council, Italy\\
\supscrsm{d}International Center for Computational Neurophotonics (ICON Foundation), Italy\\
\supscrsm{e}Integrated Research Centre, University Campus Bio-Medico of Rome, Italy\\
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{abstract}
The comprehensive mapping and quantification of neuronal projections in the central nervous system requires high-throughput imaging of large volumes with microscopic resolution. To this end, we have developed a confocal light-sheet microscope that has been optimised for the 3D imaging of structurally intact clarified whole-mount mouse brains. Here we describe the optical and electro-mechanical arrangement of the microscope and give details on the organisation of the microscope management software. The software orchestrates all components of the microscope, coordinates critical timing and synchronisation and has been written in a versatile and modular structure using the LabVIEW language.  It can easily be adapted and integrated to other microscope systems and has been made freely available to the light-sheet community. The tremendous amount of data routinely generated by light-sheet microscopy further requires novel strategies for data handling and storage. To complete the full imaging pipeline of our high- throughput microscope we further elaborate on big data management from streaming of raw images up to stitching of 3D data sets. The meso-scale neuroanatomy imaged at micron-scale resolution in those datasets allows characterization and quantification of neuronal projections in unsectioned mouse brains. 
\end{abstract}

%>>>> Include a list of up to six keywords after the abstract
\keywords{Light-sheet microscopy, whole brain imaging, data management, software management, imaging pipeline, high-throughput imaging}

%>>>> Include contact information for corresponding author
{\noindent \footnotesize{\bf Address all correspondence to}: Francesco S. Pavone, LENS, University of Florence, Via Nello Carrara 1, 50019 Sesto Fiorentino (FI), Italy; Tel: +39 055 457 2480; E-mail:  \linkable{francesco.pavone@unifi.it} }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{spacing}{2}   % use double spacing for rest of manuscript

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sect:intro}

The highly ambitious project of mapping and understanding each and every neuronal projection in the whole brain has been moved to feasible reality by the recent advent of light-sheet fluorescent microscopy (LSFM)\cite{Huisken2004,Dodt2007,Keller2012}. With this technique 3D data sets can be acquired with a resolution that is high enough to identify neurons and their dendritic and axonal features in time scales which are no longer the bottle neck of high-throughput acquisition. In LSFM, the sample is illuminated with a thin sheet of light confined into the focal plane of the detection objective, which collects the fluorescence emission along an axis perpendicular to the illumination plane\cite{Huisken2009}. This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel due to its wide-field detection and affords intrinsic optical sectioning due to the light-sheet illumination. Consequently fluorophores outside the light-sheet are neither bleached nor contribute blurring out-of-focus noise. Together these attributes cause a high spatio-temporal resolution and an excellent signal to noise ratio in LSFM.

Several challenges remain to be overcome, however, to allow fast and, most of all, systematic production of reliable datasets and their meaningful interpretation to further our understanding of neuronal networks. Those challenges include fast, cheap and reproducible sample preparation and mounting, automated image acquisition and, most crucially, storage, interpretation and analysis of the vast data sets light-sheet microscopy routinely produces\cite{Freeman2014,Burns2014}. The mapping and understanding of this ``big data" is an immense task that requires the expertise of computer scientists to employ fully automated, scalable post-processing, for example, to do blood vessel segmentation or cell counting\cite{Frasconi2014}. On the other hand, the imaging of large, intrinsically opaque samples in LSFM necessitates clearing protocols based on refractive index matching which render the tissue transparent\cite{Chung2013,Tomer2014}. Therefore technological advances in LSFM need to be matched by novel development in the area of information- and biotechnology.

Here we will present a state-of-the-art light-sheet microscope, as it is implemented in our lab, that is especially well suited to acquire 3D data sets of clarified and structurally intact mouse brains. The LSFM features double-sided illumination with a digitally scanned light-sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$) immersed and freely movable samples. After briefly introducing the optical setup we explain how to prepare and mount the samples for stable 3D imaging for several days. In addition, a full description of the control hardware and software is presented. The microscope software coordinates every microscope component and ensures critical timing and synchronisation between those components. We further give a systematic and robust approach to handle and store light-sheet microscopy data of several terabytes. To conclude the comprehensive and high-throughput imaging pipeline we furthermore elaborate on stitching of large 3D data sets. The imaging capabilities of our light-sheet microscope are exemplified with tomographies of whole transgenic mouse brains.

@@

		\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{frame1.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:excitation} (A) Schematic of the light path. The galvo scanners are mounted above periscopes. LP: long-pass filter, I: iris, AOTF: acousto-optical tunable filter, LM: laser modulator, PBS: polarisation beam splitter. Green dotted: detection path. (B) Oblique view of the microscope. A custom-made breadboard serves to mount the sample chamber and objectives at an elevated height and features two circular holes at the edges for the periscopes and a large central cut-out for the translation stages. A second breadboard is used for the camera.} 
   \end{figure}

\subsection{Laser unit}		
The custom-made confocal light-sheet microscope is equipped with five linearly polarised, continuous-wave lasers for fluorescence excitation (Fig. \ref{fig:excitation},A). The wavelengths were chosen to excite the most common fluorophores (see Table \ref{tab:optomechanics} for the manufacturer and specifications of microscope components). The beam from each laser is first collimated and expanded with a telescope made of singlet lenses (f140, f200) and then combined into a common path with a mirror and a long-pass filter (Semrock, LaserMUX\texttrademark\ series). From here on all lenses are achromatic doublets coated for the visible spectrum. An acousto-optical tunable filter (AOTF) acts as fast ($\mu s$) electronically tunable filter and intensity modulator. Due its nonlinear response we measured the AOTF light transmittance for each wavelength as a function of radio frequency amplitude and determined a look-up table to linearise the output. The zero order light is blocked by an iris. A 1:1 telescope (f150,f150) is used to re-collimate the beam after the AOTF. An electro-optical laser modulator (EOM) acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$. A digital line is used to switch between the voltage levels, allowing control of the frequency with which the polarisation is changed (see also section \ref{sec:timing} on timing).

\subsection{Illumination unit}		
The light impinges onto a polarising beam splitter cube which splits the excitation light depending on its polarisation into one of the two identical excitation arms. The beam diameter is reduced with a telescope (f350, f200) whose telecentric plane coincides with the mirrored surface of a galvanometric scanner (galvo). Both galvos are mounted on a custom made optical breadboard which features two circular holes to pass the periscopic beams and a large central cut-out for the sample chamber and motor stages (Fig. \ref{fig:excitation},B).

Each scan mirror surface is re-imaged with a telescope (f50, f100) onto the back aperture of a long working distance low magnification objective (Nikon, 10x 0.3NA WD 17.5mm). The focal lengths of the doublets making up the telescope have been chosen for space considerations and to achieve a $1/e^2$ beam radius of 0.73mm at the back focal plane resulting in an effective NA of 0.025 (see also section \ref{sec:characterisation}). The galvos are in planes conjugate with the back focal plane of their respective excitation objective to ensure that a tilt angle of the galvo converts into a lateral translation of the Gaussian beam across the specimen. The two excitation objectives are designed for air immersion but are immersed into the clearing solution (n=1.45) within the sample chamber. A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the front lens elements from the clearing agent. A guide to align objectives to a common focus can be found in the supplementary information. The light-sheet is generated digitally\cite{Keller2008a,Keller2008b} by scanning the excitation beam across the focal plane of the detection objective. This generates incoherent illumination resulting in fewer artefacts. Additionally each line in the specimen is illuminated with the same intensity creating a homogeneous light-sheet which is particularly advantageous for the quantitative and qualitative investigation of large samples in their entirety.

@@

Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions. The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP, 25x, 1.0NA, effective focal length 7.2 mm, working distance 8mm). A tube lens of 200mm creates an image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a chip of over 4 megapixels. The cell size of the OrcaFlash is $p^2= (6.5\micro m)^2$ over an active area of $r^2= (13.3mm)^2$. With a 200mm tube lens the field of view (FOV) in the sample is $(480\micro m)^2$ (see also Table \ref{tab:resolution} in the supplementary information for relevant formulas).

In the camera's rolling shutter acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor\cite{Baumgart2012}. With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($t_{\text{shutter}}=9.7\micro s$) the entire frame of 2048 horizontal lines is activated within 19.86ms. Setting the line exposure time to $t_{\text{exp}}=0.3ms$, for instance, results in $l=\nicefrac{t_{\text{exp}}}{t_{\text{shutter}}}\approx31$  lines being simultaneously exposed at any time. This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of $s_{\text{object}}=\nicefrac{l p}{M_{\text{eff}}}= 7.2 \micro m $ in the sample space, where $M_{\text{eff}}$ is the effective magnification of the detection objective. With the given values of line exposure and line read out time, the camera acquires images at a full-frame rate of  $R_{\text{frame}} = \nicefrac{1}{(\#_{\text{horiz. lines}}*t_{\text{shutter}}+t_{\text{exp}})} \approx 50Hz$.

The camera was run as master in the internal trigger mode and a synchronisation pulse generated with the exposure of each new line was used as an output trigger for a DAQ board (NI PCIe-6353, National Instruments) which was operated as slave. The saw-tooth driving signal for the galvo mirrors was generated by the DAQ and synchronised with the pixel line reset pulses from the camera to achieve confocal line detection (see also section \ref{sec:timing} on synchronisation).

\subsection{Sample mounting and motion}
\label{sec:mounting}

@@

We designed a cubic water-tight sample chamber (Fig. \ref{fig:frame2},A) that allows access from all six sides while maintaining the 3D integrity of large clarified and fluorescently labelled mouse brains. The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Fig. \ref{fig:frame2},B). Connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders. In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Fig. \ref{fig:frame2},C). The clarified brains are imaged immersed in clearing solution composed of 63\% 2,2'-thiodiethanol (TDE) in Phosphate buffered saline (PBS) and a refractive index of $n \approx 1.45$\cite{Costantini}. To fill the entire volume of the sample chamber approximately 150ml clearing solution are needed. A motorized x-, y-, z-, $\theta$-stage (see Table \ref{tab:optomechanics}) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Fig. \ref{fig:frame2},D). Illumination and detection axes are horizontal while sample rotation occurs around the vertical axis.

To elucidate neuronal projections in structurally intact tissue it is paramount to be able to image centimeter-sized clarified samples, such as mouse brains, with high resolution in whole mount preparation. The problem of sample mounting in a light-sheet microscope arises from the fact that optical access to the sample is required from 3-4 planar sides leaving only two opposing sides to insert, fix and move the sample. Stable mounting is hereby a key concern as a whole-brain tomography can require image acquisition in excess of 24 hours and the effects of gravity, tissue shrinking/expansion and evaporation of the clearing solution over such time spans might have to be considered.

For the acquisition of whole-brain data sets, we fix a clarified and fluorescently-labelled mouse brain with super glue to a coverslip (Fig. \ref{fig:frame2},E). The brain is oriented along its axial orientation with the olfactory bulbs at the top and the cerebellum at the bottom of the coverslip. The coverslip is slid into a bottom adaptor and tightened with a plastic-capped grub screw. The bottom adaptor is inserted into a Teflon cylinder with the coverslip being positioned on the far side of the detection objective. Three different slits in the adapter correspond to varying distances to the detection objective and give variability in sample thickness for example to allow also for the mounting of rat brain hemispheres.

\subsection{Optical characterisation}
\label{sec:characterisation}
\subsubsection{Theoretical considerations}

The optical properties of a microscope can be quantified by the point-spread function (PSF), which is the image of a point source in object space. The radial (i.e. perpendicular to the detection axis) and axial (i.e. parallel to the detection axis) resolution of the microscope are most commonly described by the full width at half-maximum (FWHM) of the PSF itself along the chosen direction (Fig. \ref{fig:origin},A). In a light-sheet microscope axial and radial resolution are determined by the numerical aperture (NA) of the illumination and detection optics respectively. The radial PSF is a standard Airy function whose FWHM is given by:

\begin{equation}
\text{FWHM}_{\text{radial}} \simeq \frac{0.51 \lambda_0}{\text{NA}_{\text{d}}},
\end{equation}
$\lambda_0$ being the wavelength in vacuum and $\text{NA}_{\text{d}}$ the NA of the detection objective. The axial resolution is dominated by the thickness of the light sheet which for high NA detection objectives is usually larger than the depth of field of the detection objective. If Gaussian beams are used for illumination, the thickness of the light sheet can be calculated by the well-known formulas of Gaussian optics\cite{Teich}. The radius of the beam waist is given by:

@@

\begin{equation}
\text{FWHM}_{\text{axial}} \simeq 1.177 w_0.
\end{equation}
The thickness of the light sheet is not constant throughout the FOV due to the limited depth of focus of the Gaussian beam. The latter can be quantified by the confocal parameter $b$, which is the distance along which the beam $1/e^2$ radius remains relatively constant and smaller than $\sqrt{2} w_0$:

@@

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{frame3.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:origin} Optical characterisation. (A) Exemplary lateral and axial intensity profiles of nanometric beads and fits to Gaussian curves. (B) FWHM of the Gaussian fits with confocal slit width. Each data point is the average of 10 bead profiles. (C) Signal to noise ratio (SNR) as a function of slit width.} 
\end{figure}

@@

For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) image stacks of nanometric fluorescent beads ($0.51 \micro m$ diameter, Bangs Laboratories) were acquired. The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, was not affected by the confocal slit width on the camera (Fig. \ref{fig:origin},B). The lateral and axial FWHMs were $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14) \micro m$ respectively, averaged through stack depths and confocal slit widths. The experimentally determined lateral FWHM was larger than the theoretically calculated value of $0.26 \micro m$ by a factor of four. The discrepancy is likely caused by higher order aberrations introduced by the gel embedding the fluorescent beads exacerbated by the high NA of our detection objective\cite{Schwertner2004,Schwertner2007}.

@@

\section{Data Management}
\label{sec:dataflow}
